Clicks and Cliques

### 2018-12-23 papersoul.Rnw
from qplot to ggplot in chunk import.plot2

\begin{figure}[hbpt]
<<import.plot1, dependson='data',echo=FALSE, fig.height=5,message=FALSE,warning=FALSE>>=
rankings$dim <- factor(rankings$dim)
rankings$dim <- recode(rankings$dim,"'QD2'='Residence.Years';'QD1'='Age';'Q15AB'='Lead.Int';'QD9'='Income';'Q9'='Economy';'Q8F'='Senior';'Q8D'='Children';'Q7M'='Care';'Q7L'='Leader';'Q7K'='Health';'Q7I'='Meet.People';'Q7G'='Colleges';'Q7F'='Schools';'Q7B'='Beauty';'Q6A'='5year.ahead';'Q6'='5year.ago'")

qplot(data=rankings, x=rnk,y=dim,fill=V1,geom='tile', xlab='Ranking', ylab='') +scale_fill_gradient(limits=c(0,26), low="white", high="red",name='') + theme(axis.text.y = element_text(size=I(12)) )  + theme_bw()
@
\caption{Variable importance, color intensity indicates for how many communities a variable appears in each of the first five ranks. For instance, the most important (rank equals to 1) variable is 5.year.ahead for 22 out 26 communities. \label{imp1}}
\end{figure}

@@

prodplot(aux, ~CCEGRP2+Q6A+QSB, divider=c("vspine","hspine",'hspine'),subset=level == 2)+aes(fill=CCEGRP2) + facet_wrap( facet=~QSB, scale='free',ncol=7) + theme( legend.title=element_blank(),axis.text.x=element_blank(),axis.text.y=element_blank(),  axis.title.y=element_blank(),axis.title.x=element_blank(),legend.position=c(.9,0.1) ) + scale_fill_brewer(type='seq', palette=1)
@
\caption{Product plot of attachment against forward looking variable (5.year.ahead) by community. \label{fowardplot}}
\end{figure}

@@

qplot(data=aux, x=dim2,y=QSB,fill=rmdg,geom='tile')+ theme(axis.text.x = element_text(angle=90, size=I(12)), axis.title.x=element_blank() )  +scale_fill_gradient(low="white", high="red") +theme(legend.position = 'none')
@
\caption{Illustration of the differences in important variables by community \label{imp.st}. For each variable, red intensity represent the variable relative importance, i.e. in which community that variable is more important than the average. White indicates variables below importance average.}
\end{figure}

>>>>

\begin{figure}[hbpt]
<<import.plot1, dependson='data',echo=FALSE, fig.height=5,message=FALSE,warning=FALSE>>=
rankings %>% mutate(dim = recode_factor(factor(dim),
                                        'QD2'='Residence.Years',
                                        'QD1'='Age',
                                        'Q15AB'='Lead.Int',
                                        'QD9'='Income',
                                        'Q9'='Economy',
                                        'Q8F'='Senior',
                                        'Q8D'='Children',
                                        'Q7M'='Care',
                                        'Q7L'='Leader',
                                        'Q7K'='Health',
                                        'Q7I'='Meet.People',
                                        'Q7G'='Colleges',
                                        'Q7F'='Schools',
                                        'Q7B'='Beauty',
                                        'Q6A'='5year.ahead',
                                        'Q6'='5year.ago' )) %>% 
  ggplot( aes(x = rnk, y = fct_reorder(dim, V1, max), fill = V1)) +
  geom_tile() + scale_fill_gradient(limits = c(0,26), low = "white", high = "red", name ='') +  labs( x = "Ranking", y = "") + theme(axis.text.y = element_text(size = I(12)) )  + theme_bw()

@
\caption{Variable importance, color intensity indicates for how many communities a variable appears in each of the first five ranks. For instance, the most important (rank equals to 1) variable is 5.year.ahead for 22 out 26 communities. \label{imp1}}
\end{figure}

@@

prodplot(aux, ~CCEGRP2 + Q6A + QSB, divider = c("vspine","hspine",'hspine'), subset = level == 2) + aes(fill = CCEGRP2) +
  facet_wrap( facet =~ QSB, scale = 'free', ncol = 7) +
  theme( legend.title = element_blank(),
         axis.text.x = element_blank(), axis.text.y = element_blank(),  
         axis.title.y = element_blank(),
         axis.title.x = element_blank(),
         legend.position = c(.9, 0.1) ) +
  scale_fill_brewer(type = 'seq', palette = 1)
@
\caption{Product plot of attachment against forward looking variable (5.year.ahead) by community. \label{fowardplot}}
\end{figure}

@@

ggplot(data = aux, aes(x = fct_reorder(dim2, rmdg, max), y = QSB, fill = rmdg )) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 90, size = I(12)), axis.title.x = element_blank() )  + scale_fill_gradient(low = "white", high = "red") + theme(legend.position = 'none')

@
\caption{Illustration of the differences in important variables by community \label{imp.st}. For each variable, red intensity represent the variable relative importance, i.e. in which community that variable is more important than the average. White indicates variables below importance average.}
\end{figure}
